---
layout:   post
title:    "散户之家"
category:  strategy
tags:     
    -  
    -   
description: 
published: false
status:    process
---



```{r echo=FALSE, warning=FALSE, message=FALSE}
# rm(list = ls())
library(beepr)
library(rvest)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- as.character( rep(NA,5) )          ############### No. = 10，可以修改 ################
for ( i in 1:length(url) ){
  url[i] <- paste("http://www.zf826.com/page/", i, sep="")
}

link <- function(x){
  x %>% 
  read_html() %>% 
  html_nodes(".entry-title a") %>% 
  html_attr("href")
}

all <- lapply(url, link)
```



```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[1]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[2]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[3]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[4]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][1]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][2]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][3]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][4]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][5]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][6]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][7]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][8]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][9]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][10]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][11]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][12]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][13]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][14]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`




```{r echo=FALSE, warning=FALSE, message=FALSE}
url <- all[[5]][15]
title <- url %>%
  read_html() %>%
  html_nodes(".single-title") %>% 
  html_text()

date <- url %>%
  read_html() %>%
  html_nodes(".single-meta .date") %>% 
  html_text()

main <- url %>%
    read_html()  %>% 
    html_nodes(".single-content p") %>% 
    html_text() %>% 
    paste(., collapse = '\n                                                                                              \n') %>%
    gsub("———-|———|－－－－－－|。　　|——|      |———-", "\n\n", .) %>%
    gsub("　　", "", .) %>%
    gsub("○|＞|>", "\n\n \\- ",.,) %>%
    gsub("点评：", "\n                                                                                              \n > \\**点评：\\**", .)  %>%
    gsub("传闻：|传 闻：", "\n                                                                                              \n > \\**传闻：\\**", .) 
```

### `r title`
[`r date`](`r url`)

`r main`



```{r echo=FALSE, warning=FALSE, message=FALSE}
beep()
```z